Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-04-26 tese2/16_implementation_content.tex
[ADD] starting conclusions

\subsection{Chat}
		Lastly and not less important the chat functionality was implemented using \emph{webSockets}, when a message is sent by a user, it is received by the server, which records it and sends to all the users.

>>>>

\subsection{Chat}
		Not less important the chat functionality was implemented using \emph{webSockets}, when a message is sent by a user, it is received by the server, which records it and sends to all the users.
